Blocks of extended ancestry around selected loci in hybrid zones

### 2016-02-28 drafts/hybrid_zone.tex
edits through to end of discussion

\subsection*{Future directions}

\plr{Perhaps delete this paragraph? A small note saying should check power with simulations up where we discuss the statistic would do.}
Our work has highlighted distinct genomic signatures accompanying hybrid incompatibilities. 
We suggest that such signatures could be combined in an inference framework that aims to identify incompatibilities from genome scans of hybrid zones.  
However, doing so requires careful evaluation of potential signals of an incompatibility. 
For example, should we consider jointly lengths of ancestry and allele frequencies to identify incompatibilities?
Will dividing haplotype length by the length of adjacent haplotypes add power to tests because of the extra information contained in this measure, or add noise because of chance variation in these statistics.  
Validation of the effectiveness of our proposed statistics, especially under demographic models that differ from the one dimensional hybrid zone explored above, will  provide a guide on how our results can be used to learn about selection from the distribution of ancestry tract lengths. We note, however, that power to detect regions under selection will depend on a number of parameters, such as $s$ and $T$

\plr{Remove "Future directions", title this "The hybrid filter", and discuss the hybrid filter ideas we had?}
Throughout, we have focussed on hybrid incompatibilities, however, the possibility that some loci adaptively introgress across hybrid zones has excited many biologists \citep{Arnold2004}.   
The best characterized example of adaptive introgression comes from the vitamin K epoxide reductase subcomponent 1 (vkorc1), which seems to have spread from Algerian mice \emph{Mus spretus} to house mice \emph{Mus musculus} from because it confers resistance to the anticoagulant rodenticide, warfarin. \citep{Song2011}. 
Future work could dress expected genomic signatures of adaptive introgression in hybridizing populations using the number and length of haplotypes of non-native ancestry. 
Doing so requires an understanding of how positive selection shapes ancestry block lengths in these cases.

>>>>

%\subsection*{Future directions}

%\plr{Perhaps delete this paragraph? A small note saying should check power with simulations up where we discuss the statistic would do.}
%Our work has highlighted distinct genomic signatures accompanying hybrid incompatibilities. 
%We suggest that such signatures could be combined in an inference framework that aims to identify incompatibilities from genome scans of hybrid zones.  
%However, doing so requires careful evaluation of potential signals of an incompatibility. 
%For example, should we consider jointly lengths of ancestry and allele frequencies to identify incompatibilities?
%Will dividing haplotype length by the length of adjacent haplotypes add power to tests because of the extra information contained in this measure, or add noise because of chance variation in these statistics.  
%Validation of the effectiveness of our proposed statistics, especially under demographic models that differ from the one dimensional hybrid zone explored above, will  provide a guide on how our results can be used to learn about selection from the distribution of ancestry tract lengths. We note, however, that power to detect regions under selection will depend on a number of parameters, such as $s$ and $T$

\plr{Remove "Future directions", title this "The hybrid filter", and discuss the hybrid filter ideas we had?}
\subsection*{The hybrid filter}
\alisa{Could not find a reference to the hybrid filter}

We have demonstrated here the potential utility for block length distributions in hybrid zone populations, particularly in populations that are found some distance from the center of the zone. While the focus here, has been on hybrid incompatibilities, the possibility that some loci adaptively introgress across hybrid zones has excited many biologists \citep{Arnold2004}. Future work could take a similar approach to understand how positive selection shapes ancestry block lengths, and predict  signatures of adaptive introgression in hybridizing populations using similar statistics presented here. These could eventually be combined to gain a fuller understanding of the forces shaping patterns of introgression in hybrid zones.

%The best characterized example of adaptive introgression comes from the vitamin K epoxide reductase subcomponent 1 (vkorc1), which seems to have spread from Algerian mice \emph{Mus spretus} to house mice \emph{Mus musculus} from because it confers resistance to the anticoagulant rodenticide, warfarin. \citep{Song2011}. 
%Future work could dress expected genomic signatures of adaptive introgression in hybridizing populations using the number and length of haplotypes of non-native ancestry. 
%Doing so requires an understanding of how positive selection shapes ancestry block lengths in these cases.
